A reduced representation for computational fabrication

### 2013-01-06 paper.tex
intro, previous work

\usepackage{amsfonts}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage{multirow}
\title{Spec2Fab: A  Graph-Based Framework for Fabricating Fabrication Algorithms}

@@

\section{Introduction}
Computational fabrication couples new digital manufacturing techniques with novel numerical algorithms to produce objects with remarkable physical characteristics. These methods are of great interest in computer graphics for two reasons: First, they provide us with  a new class of output devices which can render into  real-life and second, they yield valuable insight into the accuracy of our numerical models of the world.

In this paper we focus on a fundamental problem in producing any such custom object:  optimal material assignment. Given an object one must find a spatially varying material distribution that satisfies some given criteria. The algorithms that solve these problems are often complicated to develop, implement, test and modify. We provide a new graph-based framework which decomposes such problems into a small set of constituent components alleviating the above issues as well as facilitating the development and testing of new methods.

\section{Related Work} 
Here we will review previous algorithms for solving the optimal material assignment problem . We divide this review into two broad categories, optimizing for desired optical properties and optimizing for desired mechanical properties. We conclude by commenting on the similarities between these approaches.

@@

The overall contribution of our work is a flexible framework for the construction of material assignment algorithms. Our second contribution is the ``Reducer Network'',  a graphical data structure which describes both the geometric partitioning and material parameterization of  a given object. We couple this with a ``Tuner Network'' which automatically tunes the parameters of the Reducer Network to produce a fabricable object. Ultimately  we use these data structures to build an extensible, easy to use API which can produce numerous material assignment algorithms from a set of primitive operations.

>>>>

\usepackage{amsfonts}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[english]{babel}
\usepackage{hyperref}
\usepackage{multirow}
%\title{A Graph-Based Reduction for Optimal Material Assignment} 
\title{A reduced representation for computational fabrication}
% A reduced representation for computational fabrication
%\title{Spec2Fab: A Graph-Based Reduction for Computational Fabrication Algorithms}
% High-fidelity Mapping From Specification to Fabrication 
% A graph-based material assignment 
% reduction-simulation-optimization
% Exploring the space of computational fabrication algorithms

@@

\section{Introduction}

% Desktop Manufacturing is taking off
% Stress multi-material 3D printing

% The need
% Users would like to specify high-level goals for the object rather the direct specification of materials
% some examples:

% There is already of number of algorithms for specific solutions. 
% But each of them is custom, they are difficult to extend and modify, combine
% There is a general structure of these algorithms that has gone exploited: reduction, optimization, simulation
% This suggests that you can build a system for integrating/combining, but also exploring modifying individual pieces

% In our framework, we propose an optimization component that
% searches through the space of all possible device outputs
% obtained by the simulator to nd the one that best reproduces
% the desired object. Unfortunately, this search space
% is usually high-dimensional. For example, when the printing
% volume has N voxels and each of these voxels can be
% assigned to one of M base materials, the search space
% has NM dimensions. To overcome this problem, we reduce
% the search space to a lower-dimensional space using
% a reduction model.

% In this paper we propose a system (that exploits this structure) for building algorithms that compute optimal material assignment for computational fabrication
% this build around two data-strictures: the reducer network (parameterizing the space of material assignments)  and the tuner network (the data structure for specifying the optimization). We also have an API.

%Computational fabrication couples new digital manufacturing techniques with novel numerical algorithms to produce objects with remarkable physical characteristics. These methods are of great interest in computer graphics for two reasons: First, they provide us with  a new class of output devices which can render into real-life and second, they yield valuable insight into the accuracy of our numerical models of the world.

%In this paper we focus on a fundamental problem in producing any such custom object:  optimal material assignment. Given an object one must find a spatially varying material distribution that satisfies some given criteria. The algorithms that solve these problems are often complicated to develop, implement, test and modify. We provide a new graph-based framework which decomposes such problems into a small set of constituent components alleviating the above issues as well as facilitating the development and testing of new methods.

\section{Related Work}

% Computational Fabrication
% BRDFs: Weyrich, Matusik, 
% Refractive: Papas, Architectural Caustics, Finsch
% Subsurface Scattering: Dong, Hasan
% Shadows: Pauly (Shadow Art), ShadowPix
% Deformation: Face Cloning, Balloons, Bickel
% Albedo/Shading: Reliefs
% Geometry compression: Digital Bas-Relief from 3D Scenes

% Shade trees:
% abstract shade trees
% Yam, Siggraph Asia 2011

Here we will review previous algorithms for solving the optimal material assignment problem . We divide this review into two broad categories, optimizing for desired optical properties and optimizing for desired mechanical properties. We conclude by commenting on the similarities between these approaches.

@@

The overall contribution of our work is a flexible framework for the construction of material assignment for computational fabrication algorithms. Our second contribution is the ``Reducer Network'',  a graphical data structure which describes both the geometric partitioning and material parameterization of  a given object. We couple this with a ``Tuner Network'' which automatically tunes the parameters of the Reducer Network to produce a fabricable object. Ultimately  we use these data structures to build an extensible, easy to use API which can produce numerous material assignment algorithms from a set of primitive operations.
% 1. Flexible framework for material assignment
% 2. Data structures
% 3. API
